---
title: "Report on Komoot pioneers and experts in Poland"
output:
  pdf_document: default
  html_document: default
geometry: margin=0.5in
---

```{r echo = FALSE, warning = FALSE, message=FALSE, results="hide"}
library(knitr)
library(kableExtra)
source("./scraping.R")
```

My report is based on data available on page: https://www.komoot.com/pioneers/club

I have decided to prepare a short report on Komoot pioneers and experts in Poland.

I used R language and web-scraping techniques to exact information from Kommot page about polish pioneers and experts in an automated way.

In the table below, we have data about usernames and number how many pioneer and expert badges do they have. 

```{r echo = FALSE, warning = FALSE, message=FALSE}
kable(pioneers_experts) %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


Additionaly, as a small insight into our data, I will select 3 users with the highest number of expert badges. 
```{r echo = FALSE, warning = FALSE, message=FALSE}
pioneers_experts %>%
  arrange(desc(expert)) %>%
  .[1:3,]-> best_experts
kable(best_experts) %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

Undoubtedly, it's only a tip of the iceberg of facts that we can get from data...